Supporting Information:\\Conformational plasticity of phospholipid headgroups in simulations and experiments

### 2021-04-27 manuscriptPGPEsuppl.tex
Update details in SI

\noindent {\it POPG} Lipid bilayer containing 118 POPG molecules, 4110 TIP3P water molecules, and 118 potassium ions was build using CHARMM-GUI \cite{lee16}.
The system was simulated 100~ns, coupled to 298 K using Nose-Hoover~\cite{nose84,hoover85} thermostat and 1 bar with
semi-isotropic Parrinello-Rahman~\cite{parrinello81} pressure coupling.
The used default parameters and force field files from CHARMM-GUI were used.
The used files are available from \citenum{CHARMM36popg}.

\todo{Simulation details for larger simulation by A. Peon.}

\noindent {\it POPG with additional NaCl} \todo{Simulation details by A. Peon.} A pure POPG system was built with CHARMM-GUI Membrane builder [https://doi.org/10.1021/acs.jctc.5b00935]. A symmetric lipid distribution was used. The bilayer contains 500 lipids and 50 CHARMM TIP3P Water model per lipid. The simulated system was minimized, equilibrated and production run. The production simulation was 500-ns-long, which the last 100 ns were analysed.
For production simulation, a Leap-Frog algorithm was applied for integrating Newton’s equations of motion, and the LINCS algorithm was used to constrain all covalent bonds, allowing a time step of 2 fs. For water, the SETTLE method was applied. The simulation was performed in the NPT ensemble where the temperature was kept constant with the V-rescale thermostat (JCP 126, 014101, https://doi.org/10.1063/1.2408420) with water together with eventual ions and lipids coupled to separate thermostats with a coupling constant of 0.1 ps. The pressure was kept constant with a semi-isotropic scheme. The Parrinello–Rahman barostat was used to keep the pressure at 1 bar with a coupling constant of 1 ps and a compressibility of 4.6 × 10–5 bar–1. Long-range electrostatic interactions with a real-space cutoff of 1.0 nm were treated by a particle mesh Ewald scheme (PME) with a Fourier spacing of 0.12 nm and a fourth-order interpolation to the Ewald mesh. van der Waals interactions were treated with a Lennard-Jones (LJ) potential with a cutoff of 1.0 nm. Long-range dispersion correction to the pressure and energy was added.

@@

\noindent {\it POPC and POPC:POPG (7:3) mixture} \todo{Simulation details by A. Peon.} A pure POPC and POPC:POPG (7:3) mixture were built with CHARMM-GUI Membrane builder [https://doi.org/10.1021/acs.jctc.5b00935]. Bilayer contains 500 lipids and 50 CHARMM TIP3P Water model per lipid. All simulated systems were minimized, equilibrated and production run. Production simulations were 500-ns-long, which the last 100 ns were analysed.
For production simulation, a Leap-Frog algorithm was applied for integrating Newton’s equations of motion, and the LINCS algorithm was used to constrain all covalent bonds, allowing a time step of 2 fs. For water, the SETTLE method was applied. All simulations were performed in the NPT ensemble where the temperature was kept constant with the V-rescale thermostat (JCP 126, 014101, https://doi.org/10.1063/1.2408420) with water together with eventual ions and lipids coupled to separate thermostats with a coupling constant of 0.1 ps. The pressure was kept constant with a semi-isotropic scheme. The Parrinello–Rahman barostat was used to keep the pressure at 1 bar with a coupling constant of 1 ps and a compressibility of 4.6 × 10–5 bar–1. Long-range electrostatic interactions with a real-space cutoff of 1.0 nm were treated by a particle mesh Ewald scheme (PME) with a Fourier spacing of 0.12 nm and a fourth-order interpolation to the Ewald mesh. van der Waals interactions were treated with a Lennard-Jones (LJ) potential with a cutoff of 1.0 nm. Long-range dispersion correction to the pressure and energy was added.

@@

\noindent {\it POPE} Data is available at \cite{charmm36uaPOPEfiles}. CHARMM36-UA POPE simulations were performed for 200 ns using GROMACS version 5.0.6. A topology for POPE was constructed using the standard CHARMM36 all-atom PE head group combined with the original CHARMM36-UA lipid tail parameters \cite{lee14}. Simulations were performed using a hexagonal periodic box containing 336 POPE lipids. This membrane was constructed using a MARTINI force field \cite{marrink07} coarse-grained self-assembly simulation followed by reverse-mapping to an atomic resolution. Simulations were performed using standard CHARMM lipid simulation settings; further details are available at \cite{charmm36uaPOPEfiles}.

@@

\subsection{Slipids}
\noindent {\it POPE} Data is available at \cite{slipidsPOPEfiles}. Slipids POPE simulations were performed for 200 ns using GROMACS version 5.0.6. Simulations employed the original Slipids POPE parameters \cite{jambeck12b} and employed the same starting structure as the CHARMM36-UA POPE simulations. Slipids simulations employed standard AMBER force field cut-offs of 1.0 nm, previously validated for use with the Slipids force field \cite{piggot17}. Further simulation details are available at \cite{slipidsPOPEfiles}.

@@

\noindent {\it POPE} Data are available at Ref.~\citenum{bergerPOPEfiles} for Berger-POPE-2004~\cite{devries04} and at Ref.~\citenum{berger2POPEfiles} for Berger-POPE-2018~\cite{berger2POPEfiles}. Simulations of POPE membranes using the Berger force field employed two variants of the Berger force field for PE lipids. The first (Berger-POPE-2004) used the de Vries modifications which includes additional repulsive Lennard-Jones interactions on the ethanolamine hydrogen atoms. The second (Berger-POPE-2018) used this same approach but doubled the repulsive strength employed for the hydrogen atom van der Waals interactions. The latter variant results in more disorder within the membrane and a closer agreement with experimental properties such as the area per lipid of POPE. POPE simulations were performed for 200 ns using GROMACS 5.0.6 and employed a POPE membrane with 64 lipids per leaflet taken from a published GROMOS-CKP POPE membrane \cite{piggot11}. Simulations used a 1.0 nm cut-off for both electrostatic and van der Waals interactions with PME and a dispersion correction doe the energy and pressure employed respectively. Further simulation details can be found at Ref.~\citenum{bergerPOPEfiles} and at Ref.~\citenum{berger2POPEfiles}.

@@

\noindent {\it POPE} Data is available at \cite{gromos43a1s3POPEfiles}. GROMOS 43A1-S3 simulations were performed for 200 ns using GROMACS 4.0.7 employing the standard GROMOS 43A1-S3 POPE force field \cite{chiu09}. The simulation structure had 64 lipids per leaflet and was constructed from a GROMOS 43A1-S3 POPC membrane \cite{piggot12}. Simulations employed standard GROMOS 43A1-S3 settings. Further details can be found at Ref.\citenum{gromos43a1s3POPEfiles}.

@@

\noindent {\it POPE} Data is available at \cite{OPLSuaPOPEfiles}. POPE simulations with the OPLS-UA force field were performed for 200 ns using GROMACS 4.5.7. POPE parameters were constructed by modifying the OPLS-UA POPC of Ulmschneider and Ulmschneider \cite{Ulmschneider09} with standard OPLS lysine parameters. The starting membrane structure, containing 64 POPE lipids per leaflet, was created by modifying an OPLS-UA POPC membrane. Simulations employed a 1.0 nm cut-off with PME and no dispersion correction. Further simulation details can be found at \citenum{OPLSuaPOPEfiles}.

\noindent {\it POPE with vdW interaction in H (OPLS-UA/HG-H)} Data is available at \cite{OPLSuaWvdWPOPEfiles}. In addition to the OPLS simulations mentioned above, further simulations employing the same starting structure and simulation settings were employed using slightly modified parameters. These modified parameters, termed OPLS-UA/HG-H, were designed to increase the area per lipid through employing a small repulsive potential on the ethanolamine hydrogen atoms, as per the approach of de Vries with the Berger POPE parameters \cite{devries04}. Further details of these simulations can be found at Ref.\citenum{OPLSuaWvdWPOPEfiles}.

@@

\noindent {\it POPE} Data is available at \cite{gromosCKPpopeT310}. \todo{Simulation details by  A. Peon.}
A pure POPE system was built with CHARMM-GUI Membrane builder [https://doi.org/10.1021/acs.jctc.5b00935]. A symmetric lipid distribution was used. The bilayer contains 500 lipids and 50 SPC Water model per lipid. GROMOS-CKP force field was used for lipid and GROMOS54A7 for the rest. The simulated system was minimized, equilibrated and production run. The production simulation was 500-ns-long, which the last 100 ns were analysed.
For production simulation, a Leap-Frog algorithm was applied for integrating Newton’s equations of motion, and the LINCS algorithm was used to constrain all covalent bonds, allowing a time step of 2 fs. For water, the SETTLE method was applied. The simulation was performed in the NPT ensemble where the temperature was kept constant with the V-rescale thermostat (JCP 126, 014101, https://doi.org/10.1063/1.2408420) with water together with eventual ions and lipids coupled to separate thermostats with a coupling constant of 0.1 ps. The pressure was kept constant with a semi-isotropic scheme. The Parrinello–Rahman barostat was used to keep the pressure at 1 bar with a coupling constant of 1 ps and a compressibility of 4.6 × 10–5 bar–1. Long-range electrostatic interactions with a real-space cutoff of 1.0 nm were treated by a particle mesh Ewald scheme (PME) with a Fourier spacing of 0.12 nm and a fourth-order interpolation to the Ewald mesh. van der Waals interactions were treated with a Lennard-Jones (LJ) potential with a cutoff of 1.0 nm. Long-range dispersion correction to the pressure and energy was added.

@@

\noindent {\it DPPE} Data is available at \cite{gromosCKPdppe}. GROMOS-CKP DPPE simulations were performed for 500 ns using GROMACS 5.0.6. These simulations used the original GROMOS-CKP parameters \cite{piggot11} but with the charges in the ethanolamine head group taken from a GROMOS 53A6 lysine side-chain rather than a PC lipid head group, as done in the original parameters. The starting structure contained 64 lipids per leaflet and was taken from a previous GROMOS-CKP simulation \cite{piggot11}. Simulations employed standard GROMOS-CKP settings with PME employed for the long-range electrostatic interactions. Further details can be found at Ref.\citenum{gromosCKPdppe}.

\noindent {\it POPG} \todo{Simulation details by A. Peon.}
A pure L-POPG system was built with CHARMM-GUI Membrane builder [https://doi.org/10.1021/acs.jctc.5b00935]. A symmetric lipid distribution was used. The bilayer contains 500 lipids (http://pubs.acs.org/doi/abs/10.1021/jp207013v) and 50 SPC Water model per lipid with 500 sodium ions. GROMOS-CKP force field was used for lipid and GROMOS54A7 for the rest. The simulated system was minimized, equilibrated and production run. The production simulation was 500-ns-long, which the last 100 ns were analysed.
For production simulation, a Leap-Frog algorithm was applied for integrating Newton’s equations of motion, and the LINCS algorithm was used to constrain all covalent bonds, allowing a time step of 2 fs. For water, the SETTLE method was applied. The simulation was performed in the NPT ensemble where the temperature was kept constant with the V-rescale thermostat (JCP 126, 014101, https://doi.org/10.1063/1.2408420) with water together with eventual ions and lipids coupled to separate thermostats with a coupling constant of 0.1 ps. The pressure was kept constant with a semi-isotropic scheme. The Parrinello–Rahman barostat was used to keep the pressure at 1 bar with a coupling constant of 1 ps and a compressibility of 4.6 × 10–5 bar–1. Long-range electrostatic interactions with a real-space cutoff of 1.0 nm were treated by a particle mesh Ewald scheme (PME) with a Fourier spacing of 0.12 nm and a fourth-order interpolation to the Ewald mesh. van der Waals interactions were treated with a Lennard-Jones (LJ) potential with a cutoff of 1.0 nm. Long-range dispersion correction to the pressure and energy was added.
\noindent {\it POPC:POPG mixture} \todo{Simulation details by A. Peon.}

@@

Two systems of pure POPC and 50:50 POPC:POPE mixture were built using CHARMM-GUI~\cite{lee16}. They contained 128 lipids and 5120 TIP3 water molecules. The initial PDB file was modified to match OPLS-MacRog nomenclature and atom order. No ions were added. The production simulations were run for 500 ns with a time step of 2 fs. The first 200 ns were discarded for the analysis. The simulations were run with the GROMACS 2018.5~\cite{abraham2015gromacs} version. The v-rescale thermostat~\cite{bussi07} was used with a temperature of 300 K and a time constant of 0.1 ps; lipids and water were coupled separately to the heat bath. Pressure was kept constant at 1 bar using a semi–isotropic Parrinello–Rahman barostat~\cite{parrinello81} with a time constant of 4.0 ps. Long-range electrostatic interactions were calculated using the PME method~\cite{darden93,essman95}. A real space cut-off of 1.0 nm was employed with a grid spacing of 0.1 nm in the reciprocal space. Lennard-Jones potentials were cut off at 1.0 nm. All covalent bonds in lipids were constrained using the LINCS algorithm~\cite{hess07,hess97}. Water molecules were kept rigid with the SETTLE algorithm~\cite{miyamoto92}.

>>>>

\noindent {\it POPG with 118 lipids} Lipid bilayer containing 118 POPG molecules, 4110 TIP3P water molecules, and 118 potassium ions was build using CHARMM-GUI \cite{lee16}.
The system was simulated 100~ns, coupled to 298 K using Nose-Hoover~\cite{nose84,hoover85} thermostat and 1 bar with
semi-isotropic Parrinello-Rahman~\cite{parrinello81} pressure coupling.
The used default parameters and force field files from CHARMM-GUI were used.
The used files are available from \citenum{CHARMM36popg}.

\noindent {\it POPG with 500 lipids} A pure POPG system was built with CHARMM-GUI Membrane builder \cite{lee16}. A symmetric lipid distribution was used. The bilayer contains 500 lipids and 50 CHARMM TIP3P water molecules per lipid.
The 500-ns-long production simulation was performed after energy minimization and equilibration.
The last 100 ns was used for analysis.
For production simulation, a Leap-Frog algorithm was applied for integrating Newton's equations of motion, and the LINCS algorithm was used to constrain all covalent bonds, allowing a time step of 2 fs. For water, the SETTLE method was applied. The simulation was performed in the NPT ensemble where the temperature was kept constant with the V-rescale thermostat~\cite{bussi07}. Solvent and lipids were coupled to separate thermostats with a coupling constant of 0.1 ps. The pressure was kept constant with a semi-isotropic scheme. The Parrinello-Rahman barostat was used to keep the pressure at 1 bar with a coupling constant of 1 ps and a compressibility of 4.6 $\times$ 10$^5$ bar$^{-1}$. Long-range electrostatic interactions with a real-space cutoff of 1.0 nm were treated by a particle mesh Ewald scheme (PME) with a Fourier spacing of 0.12 nm and a fourth-order interpolation to the Ewald mesh. Van der Waals interactions were treated with a Lennard-Jones (LJ) potential with a cutoff of 1.0 nm. Long-range dispersion correction to the pressure and energy was added.

@@

\noindent {\it POPC and POPC:POPG (7:3) mixture} Pure POPC bilayer and POPC:POPG (7:3) mixture were built
with CHARMM-GUI Membrane builder \cite{lee16}.
Both systems contained 500 lipids and 50 CHARMM TIP3P Water model per lipid.
The 500-ns-long production simulation was performed after energy minimization and equilibration.
The last 100 ns was used for analysis.
For production simulation, a Leap-Frog algorithm was applied for integrating Newton's equations of motion, and the LINCS algorithm was used to constrain all covalent bonds, allowing a time step of 2 fs. For water, the SETTLE method was applied. All simulations were performed in the NPT ensemble where the temperature was kept constant with the V-rescale thermostat~\cite{bussi07}.
Solvent and lipids were coupled to separate thermostats with a coupling constant of 0.1 ps. The pressure was kept constant with a semi-isotropic scheme. The Parrinello-Rahman barostat was used to keep the pressure at 1 bar with a coupling constant of 1 ps and a compressibility
of 4.6 $\times$ 10$^5$ bar$^{-1}$. Long-range electrostatic interactions with a real-space cutoff of 1.0 nm were treated by a particle mesh Ewald scheme (PME) with a Fourier spacing of 0.12 nm and a fourth-order interpolation to the Ewald mesh. van der Waals interactions were treated with a Lennard-Jones (LJ) potential with a cutoff of 1.0 nm. Long-range dispersion correction to the pressure and energy was added.

@@

\noindent {\it POPE} CHARMM36-UA POPE simulations were performed for 200 ns using GROMACS version 5.0.6. A topology for POPE was constructed using the standard CHARMM36 all-atom PE head group combined with the original CHARMM36-UA lipid tail parameters \cite{lee14}. Simulations were performed using a hexagonal periodic box containing 336 POPE lipids. This membrane was constructed using a MARTINI force field \cite{marrink07} coarse-grained self-assembly simulation followed by reverse-mapping to an atomic resolution. Simulations were performed using standard CHARMM lipid simulation settings; further details and simulation data are available at Ref. \citenum{charmm36uaPOPEfiles}.

@@

\subsection{Slipids}
\noindent {\it POPE} Slipids POPE simulations were performed for 200 ns using GROMACS version 5.0.6. Simulations employed the original Slipids POPE parameters \cite{jambeck12b} and the same starting structure as the CHARMM36-UA POPE simulations. Slipids simulations employed standard AMBER force field cut-offs of 1.0 nm, previously validated for use with the Slipids force field \cite{piggot17}. Further simulation details and data are available at Ref. \citenum{slipidsPOPEfiles}.

@@

\noindent {\it POPE} 
Simulations of POPE membranes using the Berger force field employed two variants of the Berger force field for PE lipids. The first (Berger-POPE-2004) used the de Vries modifications which includes additional repulsive Lennard-Jones interactions on the ethanolamine hydrogen atoms~\cite{devries04}. The second (Berger-POPE-2018) used this same approach but doubled the repulsive strength employed for the hydrogen atom van der Waals interactions~\cite{berger2POPEfiles}. The latter variant results in more disorder within the membrane and a closer agreement with experimental properties such as the area per lipid of POPE. POPE simulations were performed for 200 ns using GROMACS 5.0.6 and employed a POPE membrane with 64 lipids per leaflet taken from a published GROMOS-CKP POPE membrane \cite{piggot11}. Simulations used a 1.0 nm cut-off for both electrostatic and van der Waals interactions with PME and a dispersion correction doe the energy and pressure employed respectively. Further simulation details can be found at Ref.~\citenum{bergerPOPEfiles} for Berger-POPE-2004 and at Ref.~\citenum{berger2POPEfiles} Berger-POPE-2018.

@@

\noindent {\it POPE} GROMOS 43A1-S3 simulations were performed for 200 ns using GROMACS 4.0.7 employing the standard GROMOS 43A1-S3 POPE force field \cite{chiu09}. The simulation structure had 64 lipids per leaflet and was constructed from a GROMOS 43A1-S3 POPC membrane \cite{piggot12}. Simulations employed standard GROMOS 43A1-S3 settings. Further details and simulation data can be found at Ref.\citenum{gromos43a1s3POPEfiles}.

@@

\noindent {\it POPE} POPE simulations with the OPLS-UA force field were performed for 200 ns using GROMACS 4.5.7. POPE parameters were constructed by modifying the OPLS-UA POPC of Ulmschneider and Ulmschneider \cite{Ulmschneider09} with standard OPLS lysine parameters. The starting membrane structure, containing 64 POPE lipids per leaflet, was created by modifying an OPLS-UA POPC membrane. Simulations employed a 1.0 nm cut-off with PME and no dispersion correction. Further simulation details and data can be found at \citenum{OPLSuaPOPEfiles}.

\noindent {\it POPE with vdW interaction in H (OPLS-UA/HG-H)} In addition to the OPLS simulations mentioned above, further simulations employing the same starting structure and simulation settings were employed using slightly modified parameters. These modified parameters, termed OPLS-UA/HG-H, were designed to increase the area per lipid through employing a small repulsive potential on the ethanolamine hydrogen atoms, as per the approach of de Vries with the Berger POPE parameters \cite{devries04}. Further details and data of these simulations can be found at Ref.\citenum{OPLSuaWvdWPOPEfiles}.

@@

\noindent {\it POPE} 
Pure POPE system was built with CHARMM-GUI Membrane builder \cite{lee16}. Symmetric lipid distribution was used. The bilayer contains 500 lipids and 50 SPC Water model per lipid. GROMOS-CKP force field was used for lipids \cite{piggot11}.
%and GROMOS54A7 for the rest.
The 500-ns-long production simulation was performed after energy minimization and equilibration.
The last 100 ns was used for analysis.
For production simulation, a Leap-Frog algorithm was applied for integrating Newton's equations of motion, and the LINCS algorithm was used to constrain all covalent bonds, allowing a time step of 2 fs. For water, the SETTLE method was applied. The simulation was performed in the NPT ensemble where the temperature was kept constant with the V-rescale thermostat \cite{bussi07}.
Solvent and lipids were coupled to separate thermostats with a coupling constant of 0.1 ps. The pressure was kept constant with a semi-isotropic scheme. The Parrinello-Rahman barostat was used to keep the pressure at 1 bar with a coupling constant of 1 ps and a compressibility of 4.6 $\times$ 10$^5$ bar$^{-1}$. Long-range electrostatic interactions with a real-space cutoff of 1.0 nm were treated by a particle mesh Ewald scheme (PME) with a Fourier spacing of 0.12 nm and a fourth-order interpolation to the Ewald mesh. van der Waals interactions were treated with a Lennard-Jones (LJ) potential with a cutoff of 1.0 nm. Long-range dispersion correction to the pressure and energy was added.
The simulation data and files are available at Ref. \citenum{gromosCKPpopeT310}.

@@

\noindent {\it DPPE} GROMOS-CKP DPPE simulations were performed for 500 ns using GROMACS 5.0.6. These simulations used the original GROMOS-CKP parameters \cite{piggot11} but with the charges in the ethanolamine head group taken from a GROMOS 53A6 lysine side-chain rather than a PC lipid head group, as done in the original parameters. The starting structure contained 64 lipids per leaflet and was taken from a previous GROMOS-CKP simulation \cite{piggot11}. Simulations employed standard GROMOS-CKP settings with PME employed for the long-range electrostatic interactions. Further details and simulation data can be found at Ref.\citenum{gromosCKPdppe}.

\noindent {\it POPG} 
A pure L-POPG system was built with CHARMM-GUI Membrane builder \cite{lee16}. A symmetric lipid distribution was used. The bilayer contains 500 lipids and 50 SPC Water model per lipid with 500 sodium ions. GROMOS-CKP force field was used for lipid \cite{piggot11} and GROMOS54A7 \cite{schmid11} for the rest.
The 500-ns-long production simulation was performed after energy minimization and equilibration.
The last 100 ns was used for analysis.
For production simulation, a Leap-Frog algorithm was applied for integrating Newton's equations of motion, and the LINCS algorithm was used to constrain all covalent bonds, allowing a time step of 2 fs. For water, the SETTLE method was applied. The simulation was performed in the NPT ensemble where the temperature was kept constant with the V-rescale thermostat \cite{bussi07}.
Solvent and lipids were coupled to separate thermostats with a coupling constant of 0.1 ps. The pressure was kept constant with a semi-isotropic scheme. The Parrinello-Rahman barostat was used to keep the pressure at 1 bar with a coupling constant of 1 ps and a compressibility of 4.6 $\times$ 10$^5$ bar$^{-1}$. Long-range electrostatic interactions with a real-space cutoff of 1.0 nm were treated by a particle mesh Ewald scheme (PME) with a Fourier spacing of 0.12 nm and a fourth-order interpolation to the Ewald mesh. Van der Waals interactions were treated with a Lennard-Jones (LJ) potential with a cutoff of 1.0 nm. Long-range dispersion correction to the pressure and energy was added.

\noindent {\it POPC:POPG mixture} \todo{Simulation details by A. Peon.}

@@

Two systems of pure POPC and 50:50 POPC:POPE mixture were built using CHARMM-GUI~\cite{lee16}. They contained 128 lipids and 5120 TIP3 water molecules. The initial PDB file was modified to match OPLS-MacRog nomenclature and atom order. No ions were added. The production simulations were run for 500 ns with a time step of 2 fs. The first 200 ns were discarded for the analysis. The simulations were run with the GROMACS 2018.5~\cite{abraham2015gromacs} version. The v-rescale thermostat~\cite{bussi07} was used with a temperature of 300 K and a time constant of 0.1 ps; lipids and water were coupled separately to the heat bath. Pressure was kept constant at 1 bar using a semi-isotropic Parrinello-Rahman barostat~\cite{parrinello81} with a time constant of 4.0 ps. Long-range electrostatic interactions were calculated using the PME method~\cite{darden93,essman95}. A real space cut-off of 1.0 nm was employed with a grid spacing of 0.1 nm in the reciprocal space. Lennard-Jones potentials were cut off at 1.0 nm. All covalent bonds in lipids were constrained using the LINCS algorithm~\cite{hess07,hess97}. Water molecules were kept rigid with the SETTLE algorithm~\cite{miyamoto92}.
